Measuring and optimizing machine learning interpretability

### 2019-03-19 2019-03-21-dagstat-imlm/dagstat-molnar.Rmd
continues talk

---
title: "Measuring and optimizing machine learning interpretability"
author: "Christoph Molnar, Giuseppe Casalicchio, Bernd Bischl"
date: "2019-03-21"
output: 
  beamer_presentation:
    includes:
      in_header: "header_pagenrs.tex"
---

@@

## Black Box problem

```{r, echo = FALSE}
knitr::include_graphics("../images/black-box.png")
```
## Problem: Tradeoff interpretability and performance
Use only interpretable models (e.g. linear model)! $\Rightarrow$ Pay with loss in performance.

```{r, echo = FALSE}
knitr::include_graphics("../images/white-box.png")
```
## Problem: Tradeoff interpretability and performance
Just use post-hoc interpretation methods (e.g. feature importance)! $\Rightarrow$ Works better for less complex models.

@@

TODO of fuzzy animal which dodges touch of hand
Or use image of cat that doges hand

@@

# The End

# Backup

## Units in Wine dataset

- fixed acidity g(tartaric acid)/dm^3^
- volatile acidity: g(acetric acid/dm^3^)
- citric acid: g/dm^3^
- residual sugar: g/dm^3^
- chlorides: g(sodium chloride)/dm^3^
- free sulfur dioxide: mg/dm^3^
- total sulfur dioxide: mg/dm^3^
- density> g/cm^3^
- pH
- sulphates: g(postassium sulphate) / dm^3^
- alcohol vol.%

>>>>

---
title: "Measuring and optimizing machine learning interpretability"
author: "Christoph Molnar, Giuseppe Casalicchio, Bernd Bischl"
date: "DagStat 2019-03-21"
institute: "LMU Munich"
output: 
  beamer_presentation:
    includes:
      in_header: "header_pagenrs.tex"
---

@@

## Black Box Problem

```{r, echo = FALSE}
knitr::include_graphics("../images/black-box.png")
```
## Problem: Tradeoff interpretability and performance
Use only interpretable models (e.g. linear model)!

$\Rightarrow$ Pay with loss in performance.

```{r, echo = FALSE}
knitr::include_graphics("../images/white-box.png")
```
## Problem: Tradeoff interpretability and performance
Just use post-hoc interpretation methods (e.g. feature importance)!

$\Rightarrow$ Works better for less complex models.

@@

```{r}
knitr::include_graphics("../images/spirit-board.jpg")
```

@@

## Interested in interpretable machine learning?
More on interpretable machine learning in my book [http://christophm.github.io/interpretable-ml-book/](http://christophm.github.io/interpretable-ml-book/).

```{r, out.width="5cm"}
knitr::include_graphics("../images/cover-bordered.jpg")
```
